A comparison of approaches to Kazakh to Kyrgyz machine translation

### 2015-02-18 2015-eamt-kazkir/2015-eamt-kazkir.tex
hargle
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59006 72bbbca6-d526-0410-a7d9-f06f51895060

>>>>

This paper presents a comparison of approaches to machine translation
from Kazakh to Kyrgyz.
The paper will be laid out as follows: Section~\ref{sec:prev}\ gives a short review of some previous work in the area of Turkic--Turkic language machine translation; Section~\ref{sec:lang} introduces Kazakh and Kyrgyz and compares their grammar;
Section~\ref{sec:sys}\ describes the systems we built and the tools used to construct them;
Section~\ref{sec:eval}\ gives an evaluation of the systems; and
finally Section~\ref{sec:conc}\ describes our aims for future work and some
concluding remarks.
